---
title: "Main Text Statistics"
author: "Forrest Jones"
output:
        html_document:
            toc: TRUE
            toc_depth: 3
            toc_float:
                  collapsed: TRUE
            theme: journal
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r getdata, echo=FALSE,message=FALSE,warning=FALSE}
source("code/utils.R")

analysis <- read_rds("data/tidy_data/analysisList.rds")

analysis.DTP <- analysis[[1]]
analysis.PCV10 <- analysis[[2]]
analysis.Rota <- analysis[[3]]

```


## Abstract

All numbers can be found in Figure 2 and Table S2

```{r}

nrow(analysis.DTP)

```

## Introduction

No numbers calculated

## Materials and Methods

### National administrative data on vaccine delivery

```{r}

distInterest <- c("Mahajanga I","MAHAJANGA I",
                  "MAROVOAY",
                  "MANAKARA-ATSIMO",
                  "toliary i","Toliary I","TOLIARY I",
                  "Toliary II","TOLIARY II",
                  "VOHIPENO"
                  )

births <- read_csv("data/raw_data/births.csv") %>%
                summarize(LiveBirths=sum(LiveBirths),
                          SurvivingInfants=sum(SurvivingInfants))
sum(births$LiveBirths)

read_csv("data/raw_data/births.csv") %>%
                  filter(District_Name %in% distInterest) %>%
                summarize(LiveBirths=sum(LiveBirths)) %>%
                mutate(percent=LiveBirths/sum(births$LiveBirths)
)

#get number of births in 2015 and 2016 for each district              
read_csv("data/raw_data/births.csv") %>%
                 filter(District_Name %in% distInterest) %>%
                  mutate(District_Name= recode(District_Name,
                                   "MAHAJANGA I"="Mahajanga I",
                                    "MAROVOAY"="Marovoay",
                                   "MANAKARA-ATSIMO"="Manakara",
                                   "toliary i"="Tulear I",
                                   "Toliary I"="Tulear I",
                                   "TOLIARY I"="Tulear I",
                                   "Toliary II"="Tulear II",
                                   "TOLIARY II"="Tulear II",
                                   "VOHIPENO"="Vohipeno"     
                                        )) %>%
                #urban
                mutate(
                        urban=ifelse(District_Name %in% c("Mahajanga I",
                                                          "Tulear I",
                                                          "Manakara"
                                                          ),1,0)) %>%
                group_by(District_Name,urban) %>%
                summarize(LiveBirths=sum(LiveBirths),
                          SurvivingInfants=sum(SurvivingInfants)) 


```

### Individual vaccination card data (VCD)

```{r}
vcard <- read_csv("data/raw_data/vaccard_final_KM.csv")
#total number of cards
nrow(vcard)

#total cards in 2015 and 2017
vcard$DDN <- as.Date(vcard$DDN,format="%m/%d/%Y")

vcard %>%  filter(DDN > as.Date("12/31/2014",format="%m/%d/%Y")) %>%
                filter(DDN < as.Date("1/1/2017",format="%m/%d/%Y")) %>%
                filter(is.na(DDN)==FALSE) %>%
                nrow()


# cards used in the analysis dataset
analysis[[1]] %>% nrow()


table(analysis.DTP$birth.year)

```


## Results

### Estimation of administrative coverage from national administrative data


```{r}

#national level coverage
natcov<-read_csv("data/raw_data/nad_data.csv", col_types = paste(rep("c",189),sep="", collapse="")) %>%
                filter(Year %in% c(2015, 2016)) %>%
                summarize(

                          DTP1=sum(as.numeric(DHHTotal),na.rm = TRUE),
                          DTP2=sum(as.numeric(DHH2Total),na.rm = TRUE),
                          DTP3=sum(as.numeric(DHH3Total),na.rm = TRUE),

                          PCV1=sum(as.numeric(Pneumo1_Total),na.rm = TRUE),
                          PCV2=sum(as.numeric(Pneumo2_Total),na.rm = TRUE),
                          PCV3=sum(as.numeric(Pneumo3_Total),na.rm = TRUE),

                          Rota1=sum(as.numeric(Rota1_Total),na.rm = TRUE),
                          Rota2=sum(as.numeric(Rota2_Total),na.rm = TRUE)

                          ) 
round(natcov/sum(births$LiveBirths),2)

```

### Estimation of vaccine coverage and timeliness from the vaccine card database

Vaccination coverage and timeliness did not always correlate....

```{r}

nrow(analysis.DTP)

weightedDF.DTP <- analysis.DTP %>% createWeightedDF()
weightedDF.PCV10 <- analysis.PCV10 %>% createWeightedDF()
weightedDF.Rota <- analysis.Rota %>% createWeightedDF()

#median for DTP
survfit(Surv(T1,D1) ~ 1, data = weightedDF.DTP)
survfit(Surv(T2, D2) ~ 1, data = weightedDF.DTP,weights=W2)
survfit(Surv(T3, D3) ~ 1, data = weightedDF.DTP,weights=W3)

#median for PCV10
survfit(Surv(T1,D1) ~ 1, data = weightedDF.PCV10)
survfit(Surv(T2, D2) ~ 1, data = weightedDF.PCV10,weights=W2)
survfit(Surv(T3, D3) ~ 1, data = weightedDF.PCV10,weights=W3)

#median for Rota
survfit(Surv(T1,D1) ~ 1, data = weightedDF.Rota)
survfit(Surv(T2, D2) ~ 1, data = weightedDF.Rota,weights=W2)

# figure 2e table
f2e_tab <- stratifyCovLat(analysis.DTP,"District")[[2]] %>%
                mutate(pLate=round(lateness,2)) %>%
                mutate(District=factor(stratum, levels=levels(analysis.DTP$District),
                                              labels= c("MAH","MAR",
                                                        "TU1","TU2",
                                                        "MAN","VOH"))) %>%
                mutate(urban = ifelse(stratum %in% c("MAHAJANGA I","MANAKARA","TULEAR I"),
                                      "Urban","Rural"),
                       urban=factor(urban,levels=c("Urban","Rural")))


f2e_tab %>% arrange(dose,pLate)

# figure 2f table
f2f_tab <-stratifyCovLat(analysis.DTP,"birth.month")[[2]] %>%
                mutate(pLate=round(lateness,2)) %>%
                mutate(birth.month=factor(as.numeric(stratum),levels=1:12))
f2f_tab %>% arrange(dose,pLate)

```

Among the children who received their first dose on time...

```{r}

late_tab <- NULL

for(d in 1:3){
        
        
        #create vaccine specific weighted df
        tmp_df <- analysis[[d]]
        tmp_df <- createWeightedDF(tmp_df)
        vax <- c("DTP","PCV10","Rota")[d]
        
        
        #second dose coverage by timeliness
        tmp_df_1ontime <- filter(tmp_df,V1.timeliness == "OnTime")
        tmp_df_1late   <- filter(tmp_df,V1.timeliness == "Late")
        
        fit_2ontime    <- survfit(Surv(T2, D2) ~ 1, 
                                  data = tmp_df_1ontime ,weights=W2)
        fit_2late    <- survfit(Surv(T2, D2) ~ 1, 
                                  data = tmp_df_1late,weights=W2)
        
        #third dose coverage by timeliness
        tmp_df_2ontime <- filter(tmp_df,V2.timeliness == "OnTime")
        tmp_df_2late   <- filter(tmp_df,V2.timeliness == "Late")
        
        fit_3ontime    <-survfit(Surv(T3, D3) ~ 1, 
                                  data = tmp_df_2ontime,weights=W3)
        fit_3late    <-survfit(Surv(T3, D3) ~ 1, 
                                  data = tmp_df_2late,weights=W3)
        
        covdf <- bind_rows(
                (1-getSurv(fit_2ontime,52)) %>%
                        mutate(
                                dose="Second",
                                timeliness="On Time"
                        ),
                (1-getSurv(fit_2late,52))%>%
                        mutate(
                                dose="Second",
                                timeliness="Late"
                        ),
                (1-getSurv(fit_3ontime,52))%>%
                        mutate(
                                dose="Third",
                                timeliness="On Time"
                        ),
                (1-getSurv(fit_3late,52))%>%
                        mutate(
                                dose="Third",
                                timeliness="Late"
                        )
                )%>%
                rename(cov=surv) %>%
                #switch upperbound and lowerbound
                rename(tmp=lb,
                       lb=ub) %>%
                rename(ub=tmp) %>%
                mutate(antigen=vax)

                late_tab <- bind_rows(covdf,late_tab)

}

late_tab %>% mutate(cov=round(cov,2),
                    ub=round(ub,2),
                    lb=round(lb,2))



```


### Evaluation of catch-up campaigns

```{r}


vwDF <- data.frame(Start= as.Date(c("2015-05-11","2015-10-28","2016-05-09")),
           End = as.Date(c("2015-05-15", "2015-11-08", "2016-05-13")))


fullobs1 <- analysis.DTP %>%
        #only include those with full follow-up time and that were vaccinated
        # filter(DDN < (last.obs-365)) %>%
        # filter(year(V1.date)==2016) %>%
        filter(V1.SA.censor==1) %>%
        #determine if first dose occurred during vaccination week
        mutate(vwStatus1=ifelse(V1.date>=vwDF$Start[1] & V1.date<=vwDF$End[1],"VW","Routine"),
               vwStatus1=ifelse(V1.date>=vwDF$Start[2] & V1.date<=vwDF$End[2],"VW",vwStatus1),
               vwStatus1=ifelse(V1.date>=vwDF$Start[3] & V1.date<=vwDF$End[3],"VW",vwStatus1)
               ) %>%
        mutate(V1.timeliness=recode(V1.timeliness,
                                    "Early"="Early/On Time",
                                    "OnTime"="Early/On Time"
                                    )) 



fullobs2 <- analysis.DTP %>%
        #only include those with full follow-up time and that were vaccinated
        # filter(DDN < (last.obs-365)) %>%
        filter(V2.SA.censor==1) %>%
        # filter(year(V2.date)==2016) %>%
        #determine if first dose occurred during vaccination week
        mutate(vwStatus2=ifelse(V2.date>=vwDF$Start[1] & V2.date<=vwDF$End[1],"VW","Routine"),
               vwStatus2=ifelse(V2.date>=vwDF$Start[2] & V2.date<=vwDF$End[2],"VW",vwStatus2),
               vwStatus2=ifelse(V2.date>=vwDF$Start[3] & V2.date<=vwDF$End[3],"VW",vwStatus2),
               
               vwStatus3=ifelse(V3.date>=vwDF$Start[1] & V3.date<=vwDF$End[1],"VW","Routine"),
               vwStatus3=ifelse(V3.date>=vwDF$Start[2] & V3.date<=vwDF$End[2],"VW",vwStatus3),
               vwStatus3=ifelse(V3.date>=vwDF$Start[3] & V3.date<=vwDF$End[3],"VW",vwStatus3)
               ) %>%
        mutate(V2.timeliness=recode(V2.timeliness,
                                    "Early"="Early/On Time",
                                    "OnTime"="Early/On Time"
                                    ))


fullobs3 <- analysis.DTP %>%
        #only include those with full follow-up time and that were vaccinated
        # filter(DDN < (last.obs-365)) %>%
        filter(V3.SA.censor==1) %>%
        # filter(year(V3.date)==2016) %>%
        #determine if first dose occurred during vaccination week
        mutate(vwStatus3=ifelse(V3.date>=vwDF$Start[1] & V3.date<=vwDF$End[1],"VW","Routine"),
               vwStatus3=ifelse(V3.date>=vwDF$Start[2] & V3.date<=vwDF$End[2],"VW",vwStatus3),
               vwStatus3=ifelse(V3.date>=vwDF$Start[3] & V3.date<=vwDF$End[3],"VW",vwStatus3)
               ) %>%
        mutate(V3.timeliness=recode(V3.timeliness,
                                    "Early"="Early/On Time",
                                    "OnTime"="Early/On Time"
                                    ))

#investigation of number of doses given during vaccination week
ftdf1 <- bind_rows(fullobs1 %>%
                        group_by(vwStatus1,V1.timeliness) %>%
                        summarize(count=n()) %>%
                        mutate(dose="First")%>%
                        rename(vwStatus=vwStatus1) %>%
                        spread(V1.timeliness,count),
                  fullobs2 %>%
                        group_by(vwStatus2,V2.timeliness) %>%
                        summarize(count=n())%>%
                        mutate(dose="Second")%>%
                        rename(vwStatus=vwStatus2)%>%
                        spread(V2.timeliness,count),
                  fullobs3 %>%
                        group_by(vwStatus3,V3.timeliness) %>%
                        summarize(count=n())%>%
                        mutate(dose="Third") %>%
                        rename(vwStatus=vwStatus3) %>%
                        spread(V3.timeliness,count),
                  )  %>% 
        mutate(Total=`Early/On Time`+Late,
               `Percent Late`=round(Late/Total*100,1)) %>%
        rename(Dose=dose,
               Type=vwStatus)

ftdf1[,c(2,1,3:6)] %>% flextable() %>% autofit()

#investigation of TTV

ftdf2 <- bind_rows(
        
        fullobs1 %>% group_by(vwStatus1)%>%
        summarize(medianTTV=median(B1.SA.time),
                       lqTTV=quantile(B1.SA.time,0.25),
                       uqTTV=quantile(B1.SA.time,0.75)
                       ) %>%
        mutate(Dose="First") %>%
        rename(Type=vwStatus1),

        fullobs2 %>% group_by(vwStatus2)%>%
                summarize(medianTTV=median(B2.SA.time),
                               lqTTV=quantile(B2.SA.time,0.25),
                               uqTTV=quantile(B2.SA.time,0.75)
                               ) %>%
                mutate(Dose="Second")%>%
                rename(Type=vwStatus2),

        fullobs3 %>% group_by(vwStatus3)%>%
                summarize(medianTTV=median(B3.SA.time),
                               lqTTV=quantile(B3.SA.time,0.25),
                               uqTTV=quantile(B3.SA.time,0.75)
                               ) %>%
                mutate(Dose="Third")%>%
                rename(Type=vwStatus3)
) %>% mutate(
        medianTTV=round(medianTTV,1),
        lqTTV = round(lqTTV,1),
        uqTTV = round(uqTTV,1)
) %>%
        mutate("Median Time to Vaccination (IQR)" =paste0(medianTTV," (",
                                                           lqTTV,"-",uqTTV,")")) %>%
        select(-medianTTV,-lqTTV,-uqTTV)

ftdf2[,c(2,1,3)] %>% flextable()  %>% autofit()

```

### Simulation of catch-up campaigns

```{r}
hazard <- getRates(analysis.DTP,1) %>% rename(rate1=prob) %>%
        left_join(getRates(analysis.DTP,2) %>% rename(rate2=prob)) %>%
        left_join(getRates(analysis.DTP,3) %>% rename(rate3=prob)) %>%
         mutate(rate2=ifelse(is.na(rate2),0,rate2),
                rate3=ifelse(is.na(rate3),0,rate3)
                ) 
catchupNone <- VWsimulation(catchup = 0,   rates=hazard)

summary(catchupNone[[1]])


```


## Discussion

No text to check here

